\section{Unscented Transformation}
\label{appendix:unscented}
In this section we outline the full unscented sampling procedure.
First, we remark that ALTRO does not natively support complex numbers, so our optimization
is performed under an isomorphism 
$\mathcal{H}(\mathbb{C}^{n}) \cong \mathcal{H}(\mathbb{R}^{2n})$
\cite{leung2017speedup}. 
\todo{this should probably be mentioned explicitly in the main body of the paper. Also 
make sure you're being consistent on your definition of $n$. The definition here doesn't seem 
to match your definition other places, especially when you start augmenting the dynamics.}
\begin{equation}
  H \psi \cong \begin{pmatrix} H_{\textrm{re}} & -H_{\textrm{im}} \\ H_{\textrm{im}} & H_{\textrm{re}}\end{pmatrix}
  \begin{pmatrix} \psi_{\textrm{re}} \\ \psi_{\textrm{im}}\end{pmatrix}
\end{equation}

The unscented sampling method concerns a quantum state $\psi \in \mathbb{R}^{2n}$ with
deviant parameters $\lambda \in \mathbb{R}^{d}$ and dynamics $\psi_{k + 1} = f(\psi_{k}, \lambda_{k})$.
The nominal initial quantum state is given by $\psi_{0}$ with an associated
positive-definite covariance matrix $P_{0} \in \mathbb{R}_{++}^{n \times n}$
which describes the uncertainty in the initial state.
$P_{0}$ is typically chosen to be non-zero even if the state preparation error is negligible.
The deviant parameter
is assumed to have zero mean and its distribution is given by the covariance matrix
$L_{k} \in \mathbb{R}_{++}^{d \times d}$ at knot point $k$. The zero mean assumption
is convenient for deriving the update procedure. A non-zero mean can be encoded
in the dynamics $f$.

The initial $4n + 2d$ sigma points and initial $4n + 2d$ deviant parameters are sampled
from the initial distributions
\begin{equation}\label{eq:uupdate}
  \begin{bmatrix} \Psi_{0}^{i} \\ \Lambda_{0}^{i} \end{bmatrix} =
  \begin{bmatrix} \bar{\Psi}_{0} \\ 0\end{bmatrix}
    \pm \beta \sqrt{\begin{bmatrix} P_{0} & 0\\ 0 & L_{0}\end{bmatrix}}^{\; i}
\end{equation}
We have written $\bar{\Psi}_{0} = \psi_{0}$. $\beta$
is a hyperparameter which controls the spacing of the covariance contour.
The $(\pm)$ is understood to take $(+)$ for $ i \in \{1, \dots, 2n + d\}$ and $(-)$ for
$i \in \{2n + d + 1, \dots, 4n + 2d\}$. We use the Cholesky factorization
to compute the square root of the
joint covariance matrix, though other methods
such as the principal square root may be employed.
The superscript on the matrix square root indicates the $i$\textsuperscript{th}
column (mod $2n + d$) of the lower triangular Cholesky factor.
Then, the sigma points are normalized
\begin{equation}\label{eq:unormalize}
  \Psi_{0}^{i} \gets \frac{\Psi_{0}^{i}}{\sqrt{\Psi_{0}^{i^{T}} \Psi_{0}^{i}}}
\end{equation}
The sigma points are propagated to the next knot point
\begin{equation}\label{eq:upropagate}
  \Psi_{1} = f(\Psi_{0}, \Lambda_{0})
\end{equation}
The mean and covariance of the sigma points are computed
\begin{align}
  \bar{\Psi}_{1} &= \frac{1}{4n + 2d} \sum_{i = 1}^{4n + 2d} \Psi_{1}^{i}\\
  P_{1} &= \frac{1}{2 \beta^{2}} \sum_{i = 1}^{4n + 2d}
  (\Psi^{i}_{1} - \bar{\Psi}_{1})^{T}(\Psi^{i}_{1} - \bar{\Psi}_{1})
\end{align}
The sigma points are then resampled and propagated to the next knot point using
\eqref{eq:uupdate}, \eqref{eq:unormalize}, and \eqref{eq:upropagate}. Our
choice of sigma points follows the prescription in equation 11 of \cite{julier2004unscented}.
Other prescriptions may be chosen to reduce the number of required sigma points \cite{julier2002reduced}.




